---
title: "GR5205_HW3_Multilinear Regression"
author: "Jennifer Lieu"
date: "10/22/2018"
output:
  pdf_document: default
  html_document: default
---

Problem 3:
```{r}
#load dataset
setwd("/Users/jenniferlieu/Desktop/Linear Regression Models Data 1")
hw3 <- read.table("HW3Problem3.txt", header=T)

#set dataset into dataframe
hw3[[1]] <- unlist(as.numeric(hw3[[1]]))
hw3[[2]] <- unlist(as.numeric(hw3[[2]]))
hw3[[3]] <- unlist(as.numeric(hw3[[3]]))
hw3[[4]] <- unlist(as.numeric(hw3[[4]]))
hw3[[5]] <- unlist(as.numeric(hw3[[5]]))
```

3.1
```{r}
fullmodel <- lm(hw3[[1]]~hw3[[2]]+hw3[[3]]+hw3[[4]]+hw3[[5]])
#coefficients of linear model shown below
fullmodel
```

3.2 and 3.3
```{r}
summary(lm(hw3[[1]]~hw3[[2]]+hw3[[3]]+hw3[[4]]+hw3[[5]]))
```
5847% of the variation of the rental rates were explained by this model.
Due to the high P(>|t|) values for each beta, we conclude that all the marginal relationships between the response variable and covariate work except the one for x3.

3.4
```{r}
reducedmodel1 <- lm(hw3[[1]]~1)
anova(reducedmodel1, fullmodel)
```
Because 7.272e-14<.05, we reject the null hypothesis at the 5% significance level thatthere is an overall relationship between the rental rates and all
of the covariates. 

3.5
```{r}
reducedmodel2 <- lm(hw3[[1]]~hw3[[3]]+hw3[[5]])
anova(reducedmodel2, fullmodel)
```
Because 1.003e-08<.05, we reject the null hypothesis at the 5% significance level that the coefficients of X1 and X3 are not zero. 

3.6
```{r}
reducedmodel3 <- lm(hw3[[1]]~hw3[[2]]+hw3[[3]]+hw3[[5]])
anova(reducedmodel3, fullmodel)
```

Because 0.5704>.05, cannot reject the null hypothesis at the 5% significance level that the coefficient of X3 are not zero.The p-values are the same between the marginal t test, and the f test.

3.7
```{r}
fullmodel1 <- lm(RentalRates~Age+OperatingExpense+VacancyRates+SquareFootage, data=hw3)

X.h <- data.frame(Age=5.0, OperatingExpense=8.25, VacancyRates=0, SquareFootage=250000)
predict(fullmodel1,X.h,interval = "confidence", level= .9875)

X.h <- data.frame(Age=6.0, OperatingExpense=8.50, VacancyRates=0.23, SquareFootage=270000)
predict(fullmodel1,X.h,interval = "confidence", level= .9875)

X.h <- data.frame(Age=14.0, OperatingExpense=11.50, VacancyRates=0.11, SquareFootage=300000)
predict(fullmodel1,X.h,interval = "confidence", level= .9875)

X.h <- data.frame(Age=12.0, OperatingExpense=10.25, VacancyRates=0, SquareFootage=310000)
predict(fullmodel1,X.h,interval = "confidence", level= .9875)
```

Problem 4:
```{r}
hw4 <- read.table("HW3Problem4.txt")
x<-hw4$x
y<-hw4$y
x1<-x
x2<-x^2
x3<-x^3
ymodel<- lm(y~x1+x2+x3)
ymodel

z<- c(0:16)
plot(y~x)
lines(0:16,y=16.9729 + 88.1660*z - 18.0874*z*z +  0.9155*z*z*z, col="Red", add=TRUE)
```
